\LARGE \bf IMU-based pose-estimation for spherical robots with limited resources

### 2021-09-07 mfi21/ieeeconf/root.tex
shortend to 8 side
above -> left:

\overrideIEEEmargins                                      % Needed to meet printer requirements.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{siunitx}
%\usepackage{enumitem}
\newcommand{\M}[1]{\mathbf{#1}} % Bold for matrix
\newcommand{\V}[1]{\mathbf{#1}} % Bold for vector
%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a contents stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
%\pdfminorversion=4

@@

This behavior is most prominent during standstill as the Madgwick filter was designed for movement.

@@

\begin{figure}
\includegraphics[width=\linewidth]{./graphics/MadgwickVsComplementaryNoMovement.eps}
\caption{Quaternion values of Madgwick filter and complementary filter with default gains when IMU is at a standstill. The Madgwick filter has clearly visible jitter, the complementary filter has not.}
\label{madgVsComp1}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{./graphics/jasperhome1.png} \\
\vspace{0.2cm}
\includegraphics[width=\linewidth]{./graphics/jasperhome1madw.png}
\caption{Above: resulting 3D map using the presented algorithm for pose filtering. Below: resulting 3D map using Madgwick + double integrator for pose filtering. Both images were shot from the exact same point of view. Both plots use the same LIDAR data and apply one of the simultaneously generated pose estimations.}
\label{fig:mapping}
\end{center}
\end{figure}

>>>>

\overrideIEEEmargins                                      % Needed to meet printer requirements.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{units}
%\usepackage{enumitem}
\newcommand{\M}[1]{\mathbf{#1}} % Bold for matrix
\newcommand{\V}[1]{\mathbf{#1}} % Bold for vector
%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a contents stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
%\pdfminorversion=4

@@

This jittering behavior is most prominent during standstill as the Madgwick filter was designed for movement.

@@

\begin{figure}
%\includegraphics[width=\linewidth]{./graphics/MadgwickVsComplementaryNoMovement.eps}
\makebox[\linewidth][c]{\includegraphics[width=1.15\linewidth]{./graphics/CompelemntaryVsMadgwick6seconds.eps}}
\caption{Quaternion values of Madgwick filter and complementary filter with default gains when IMU is at a standstill. The Madgwick filter has clearly visible jitter, the complementary filter has not.}
\label{madgVsComp1}
\end{figure}

@@

\begin{figure}
%\begin{center}
\includegraphics[width=0.52\linewidth]{./graphics/jasperhome1.png} 
%\vspace{0.2cm}
\includegraphics[width=0.45\linewidth]{./graphics/jasperhome1madw.png}
\caption{Left: resulting 3D map using the presented algorithm for pose filtering. Right: resulting 3D map using Madgwick + double integrator for pose filtering. Both images were shot from the exact same point of view. Both plots use the same LIDAR data and apply one of the simultaneously generated pose estimations.}
\label{fig:mapping}
%\end{center}
\end{figure}
